\thispagestyle{empty}

For office use only \,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,
Team Control Number \,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,
For office use only

\begin{singlespace}
T1\,\uline{\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,
}\textbf{\Large{}\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,77824\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\hspace{0.11cm}\,\,\,\,\,\,}F1\,\uline{\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\, }

T2\,\uline{\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,
}\textbf{\Large{}\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,
\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\hspace{0.17cm}\,\,\,\,\,\,\,\,}F2\,\uline{\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\, }

T3\,\uline{\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,
}\textbf{\Large{}\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,}Problem
Chosen\textbf{\Large{}\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\hspace{0.17cm}\,\,\,\,}F3\,\uline{\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\, }

T4\,\uline{\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,
}\textbf{\Large{}\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,A\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,}F4\,\uline{\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\, }
\end{singlespace}

\noindent \rule{1\columnwidth}{0.5pt}
\noindent \begin{center}
\textbf{2019 Mathematical Contest in Modeling(MCM) Summary Sheet}
\par\end{center}

\noindent \begin{center}
\textbf{Title of the Paper}
\par\end{center}
\begin{abstract}
HF radio waves will reflect several times between ionosphere and ocean
surface to spread the information in a special direction. However,
the characteristics of the ocean surface will influence its propagation
a lot, which will complicate the situation.In order to study the rules
of the transmission of HF radio waves, we first analyze the loss in
each process, including launching, receiving and propagating. Next,
we build three sub-models to discuss the three main processes in the
sky-wave transmission.

In Sub-model I, we analyze the reflection and transmission of HF radio
waves in ionosphere. We can calculate the value of MUF in a given
condition, which is 10.99Hz. Our sub-model manifests that the higher
the frequency of HF radio waves and the smaller the angle of incidence,
the far less the loss caused by ionosphere.

In Sub-model II, we discuss the differences of the reflection on between
the calm and turbulent ocean surface. In the calm ocean situation,the
loss is extremely small because the Fresnell reflection coefficient
nearly equals to 1.Yet in the turbulent ocean, we can merely consider
it as diffuse. Aimed to simplify the model, we take advantage of the
sine function to simulate the shape of ocean waves, and get the probable
density of reflection power in different angles.We find the reflection
power on the turbulent surface is almost 100 times smaller than that
on calm surface. 

In Sub-model III, we tend to consider a signal received by the ship
in the turbulent ocean. First we assume a situation in the twodimensional
space. Comparing to the signal reception on the calm ocean, we find:
1 the receivable distance will be shorter. 2 the receiving power intensity
is unstable because the ocean is choppy causing the swing of the antenna. 

The sensitivity analysis of our model has pointed out that the MUF
varies in different periods while the value is greater in the daytime
and smaller at night. Also we find that the height of the ocean waves
is not an important factor for the power of reflecting radio waves.
\end{abstract}

